### 2016-08-30 README.Rmd
improve readme

>>>>

## Installation

To install `MSnbase`

```{r install, eval = FALSE}
library("BiocInstaller")
biocLite("MSnbase")
```

If you need the github version

```{r installgh, eval = FALSE}
biocLite("lgato/MSnbase")
```

## Questions

General questions should be asked on the
[Bioconductor support forum](https://support.bioconductor.org/), using
`MSnbase` to tag the question.

## Citation
